The paper on \Large \bf Blockchain Frontrunning

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] add fig submarine

The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}.

>>>>

The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.
